Automated verification of stand-alone solar photovoltaic systems

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed sections 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%
%\begin{figure}[h]
%\includegraphics[width=0.5\textwidth]{statetransition}
%\centering
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%\end{figure}
%
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
%
The flowchart of the automated verification proposed is illustrated in Fig.\ref{fig:flowchartgeneral}. 
The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as C Programming language code.

@@

The weather data (solar irradiance, and ambient temperature by default) will suffer a heavy test at ESBMC run-time execution, based in maximum and minimum values from the site where the PV system will be deployed. In addition, depending if one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system, is not accomplished or satisfied, the tool accuses a fail, and the diagnostic counterexample shows in which condition the fail/violation happened. 
%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
% (as reliability, performance, or safety)

Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements, the tool will verify if the requirements of the solar PV project are met. Detailing the condition of violation, i.e., the state of each variable related to the system.

\subsection{The case studies and the Algorithm}
It was performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h). 
%and as backup at night 
%
%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
%
%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
%
%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).

@@

Algorithm 1 describes the pseudo code used to perform the automated verification.

@@

  \STATE $SOC \leftarrow SOC - 16\,h\, discharge$
  \STATE $AutonomyCount \leftarrow 16$
  \\  
    \COMMENT {autonomy of 16:00h-08:00h discharge period}
  \\
  \STATE assert ($SOC \geq SOC_{limit}$)  
  \\
  \COMMENT {Perform same 08:00h-16:00h \textbf{for}-LOOP as line 6}
  %%\ENDFOR
  \ENDWHILE
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \end{algorithm}

>>>>

%
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%
%\begin{figure}[h]
%\includegraphics[width=0.5\textwidth]{statetransition}
%\centering
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%\end{figure}
%
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
%
The flowchart of the proposed (automated) verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \textcolor{red}{add citation here to the standard}.

@@

The weather data (solar irradiance, and ambient temperature by default) will be evaluated by the ESBMC verification engine, based on maximum and minimum values from the site, where the PV system will be deployed. In addition, depending on one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system to check whether it is not accomplished or satisfied, the tool accuses a failure, and the diagnostic counterexample shows in which condition the fail/violation happened. 
%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
% (as reliability, performance, or safety)

\textcolor{red}{I didn't understand this sentence... it is completely broken...} Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements, the tool will verify if the requirements of the solar PV project are met. Detailing the condition of violation, i.e., the state of each variable related to the system.

%---------------------------------------------------------------------
\subsection{The case studies and the Algorithm}
%---------------------------------------------------------------------

We performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h). 
%and as backup at night 
%
%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
%
%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
%
%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).

@@

Algorithm~\ref{alg:verification-algorithm} describes the pseudo code used to perform the automated verification. \textcolor{red}{Can you please briefly explain this algorithm?}

@@

  \STATE $SOC \leftarrow SOC - 16\,h\, discharge$
  \STATE $AutonomyCount \leftarrow 16$
  \\  
    \COMMENT {autonomy of 16:00h-08:00h discharge period}
  \\
  \STATE assert ($SOC \geq SOC_{limit}$)  
  \\
  \COMMENT {Perform same 08:00h-16:00h \textbf{for}-LOOP as line 6}
  %%\ENDFOR
  \ENDWHILE
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}
